---
title: "Semantic inaccessibility and interference: eye-tracking models"
author: anonymous
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r cod1, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}

here::i_am("doc/models_summary.Rmd")

library(here)
library(tibble)
library(knitr)
library(dplyr)
library(purrr)
library(readr)
library(fs)

source(here("src/04-models_summary.R"))
source(here("src/03-models.R"))

dfs <- list.files(here("results"), pattern = "region[0-9].csv") %>%
  map(~ read_csv(here("results", .)))

opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
               results = "asis", fig.path = here("figs/"), cache = TRUE)
options(digits = 5)
  ## "[a-z]+_(full)|(split)_[a-z_86]+.csv"
res <- dir_ls(here("results"), regexp = "[a-z]{2,}_((nested)|(full))") %>%
  map_dfr(read_csv, .id = "source") %>%
  mutate(source = path_file(source))
```

> ‘The professor has [a/no] [son/daughter]. The past few years, [he/she] unfortunately had to work during all the holidays.

there are 8 means in the experiment (quantifier, subject, object conditions):

| quantifier | subject (typicality) | object (interference) | alternative name  | stimuli                      |
|:----------:|:--------------------:|:---------------------:|:-----------------:|:----------------------------:|
| EEN        | MATCH                | MATCH                 | (typical, int)    | prof ... a son ... he        |
| EEN        | MATCH                | MIS                   | (typical, noint)  | prof ... a daughter ... he   |
| EEN        | MIS                  | MATCH                 | (atypical, int)   | prof ... a daughter ... she  |
| EEN        | MIS                  | MIS                   | (atypical, noint) | prof ... a son ... she       |
| GEEN       | MATCH                | MATCH                 | (typical, int)    | prof ... no son ... he       |
| GEEN       | MATCH                | MIS                   | (typical, noint)  | prof ... no daughter ... he  |
| GEEN       | MIS                  | MATCH                 | (atypical, int)   | prof ... no daughter ... she |
| GEEN       | MIS                  | MIS                   | (atypical, noint) | prof ... no son ... she      |

Contrasts for the "base" models:

```{r contrasts-table }
dfs[[1]] %>%
  group_by(quan_cond, typic_cond, interf_cond) %>%
  summarise(quants_contrast = first(quants),
            subj_contrast = first(typic),
            obj_contrast = first(interf)) %>%
  mutate("quant x subj" = quants_contrast * subj_contrast,
         "quant x obj" = quants_contrast * obj_contrast,
         "subj x obj" = subj_contrast * obj_contrast,
         "quant x subj x obj" = quants_contrast * subj_contrast * obj_contrast,
         ## subj
         typic_cond = if_else(typic_cond == "atypical",
                              "mis", "match"),
         ## obj
         interf_cond = if_else(interf_cond == "interf",
                               "match", "mis"),
         "condition (quant, subj, obj)" = paste(casefold(quan_cond),
                                                typic_cond, interf_cond,
                                                sep = ", ")) %>%
  relocate("condition (quant, subj, obj)") %>%
  ungroup() %>%
  select(-c(quan_cond:interf_cond)) %>%
  rename(quantifier = quants_contrast, subject = subj_contrast,
         object = obj_contrast) %>%
  ## this is to generate the latex table
  ## select(starts_with("condition"):object) %>%
  ## kable(format = "latex")
  kable()
```

Contrasts for the nested models:

```{r nested-contrasts }

dfs[[1]] %>%
  mutate(subj_een = case_when(
        subj_cond == "MATCH" & obj_cond == "MATCH" & quan_cond == "EEN" ~ 1,
        subj_cond == "MATCH" & obj_cond == "MIS" & quan_cond == "EEN" ~ 1,
        subj_cond == "MIS" & obj_cond == "MATCH" & quan_cond == "EEN" ~ -1,
        subj_cond == "MIS" & obj_cond == "MIS" & quan_cond == "EEN" ~ -1,
        quan_cond == "GEEN" ~ 0
      ),
      obj_een = case_when(
        subj_cond == "MATCH" & obj_cond == "MATCH" & quan_cond == "EEN" ~ 1,
        subj_cond == "MATCH" & obj_cond == "MIS" & quan_cond == "EEN" ~ -1,
        subj_cond == "MIS" & obj_cond == "MATCH" & quan_cond == "EEN" ~ 1,
        subj_cond == "MIS" & obj_cond == "MIS" & quan_cond == "EEN" ~ -1,
        quan_cond == "GEEN" ~ 0
      ),
      subj_geen = case_when(
        subj_cond == "MATCH" & obj_cond == "MATCH" & quan_cond == "GEEN" ~ 1,
        subj_cond == "MATCH" & obj_cond == "MIS" & quan_cond == "GEEN" ~ 1,
        subj_cond == "MIS" & obj_cond == "MATCH" & quan_cond == "GEEN" ~ -1,
        subj_cond == "MIS" & obj_cond == "MIS" & quan_cond == "GEEN" ~ -1,
        quan_cond == "EEN" ~ 0
      ),
      obj_geen = case_when(
        subj_cond == "MATCH" & obj_cond == "MATCH" & quan_cond == "GEEN" ~ 1,
        subj_cond == "MATCH" & obj_cond == "MIS" & quan_cond == "GEEN" ~ -1,
        subj_cond == "MIS" & obj_cond == "MATCH" & quan_cond == "GEEN" ~ 1,
        subj_cond == "MIS" & obj_cond == "MIS" & quan_cond == "GEEN" ~ -1,
        quan_cond == "EEN" ~ 0
      )) %>%
  group_by(quan_cond, typic_cond, interf_cond) %>%
  summarise(subj_een = first(subj_een),
            obj_een = first(obj_een),
            subj_geen = first(subj_geen),
            obj_geen = first(obj_geen)) %>%
  mutate(## subj
    typic_cond = if_else(typic_cond == "atypical",
                              "mis", "match"),
         ## obj
         interf_cond = if_else(interf_cond == "interf",
                               "match", "mis"),
         "condition (quant, subj, obj)" = paste(casefold(quan_cond),
                                                typic_cond, interf_cond,
                                                sep = ", ")) %>%
  ungroup() %>%
  select(-c(quan_cond:interf_cond)) %>%
  relocate("condition (quant, subj, obj)") %>%
  kable()
```

On the plots the thick line signifies the 0.5 probability interval, the thin line probability of 0.95.
Note that the region numbers are a bit misleading. Consult the table below (region number 7 is missing):

| Number in the dataset | Description                     | Name in the paper / comments                   |
|:---------------------:|:-------------------------------:|:----------------------------------------------:|
| 1                     | subject                         | -                                              |
| 2                     | verb                            | -                                              |
| 3                     | object                          | -                                              |
| 4                     | wrap-up of first sentence       | not  present in   all  stimuli,  not  analyzed |
| 5                     | introduction of second sentence | pre-critical region                            |
| 6                     | verb + pronoun                  | critical region                                |
| 8                     | 3 words  spillover              | post-critical region                           |
| 9                     | wrap-up of  second  sentence    | wrap-up region                                 |

## Total fixation duration

Total fixations, all regions.

```{r tot }
res %>%
  filter(source == "totfixdur_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps1, results = "markup" }
post_plots("totfixdur", dfs, .return = "full_models")
post_plots("totfixdur", dfs, make_plot_func = pp_check, .return = "full_models")
```

### Nested models

Effects of subj and obj nested within each quantifier.

```{r tot2 }
res %>%
  filter(source == "totfixdur_nested_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps2, results = "markup" }
post_plots("totfixdur", dfs, .return = "nested_models")
## post_plots("totfixdur", dfs, make_plot_func = pp_check)$split_models
```


## Re-reading duration

Data was excluded when the participant did not re-read the region.


```{r rrdur }
res %>%
  filter(source == "rrdur_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_rrdur, results = "markup" }
post_plots("rrdur", dfs, .return = "full_models")
post_plots("rrdur", dfs, make_plot_func = pp_check, .return = "full_models")
```

### Nested models

Effects of subj and obj nested within each quantifier.

```{r rrdur2 }
res %>%
  filter(source == "rrdur_nested_models.csv") %>%
  select(-source) %>%
  kable()
```


```{r pps_rrdur2, results = "markup" }
post_plots("rrdur", dfs, .return = "nested_models")
post_plots("rrdur", dfs, make_plot_func = pp_check, .return = "nested_models")
```

## First pass regression path

There were problems with fitting the `rpdur` measure. So currently we don't have a model for that.

## First pass


First pass first gaze, `gdur`. Region 5 and the following ones (e.g. starting on critical).
Note that fits for regions 6 and 8 are a bit off.

```{r gdur }
res %>%
  filter(source == "gdur_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_gdur, results = "markup" }
post_plots("gdur", dfs[seq(5,8)], .return = "full_models")
post_plots("gdur", dfs[seq(5,8)], make_plot_func = pp_check, .return = "full_models")
```


### Nested models


Effects of subj and obj nested within each quantifier.

```{r gdur2 }
res %>%
  filter(source == "gdur_nested_models.csv") %>%
  select(-source) %>%
  kable()
```


```{r pps_gdur2, results = "markup" }
post_plots("gdur", dfs[seq(5,8)], .return = "nested_models")
post_plots("gdur", dfs[seq(5,8)], make_plot_func = pp_check, .return = "nested_models")
```


## Right bounded

Aka first pass total gaze, `tgdur`. Note that region 6 fit badly.


```{r tgdur }
res %>%
  filter(source == "tgdur_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_tgdur, results = "markup" }
post_plots("tgdur", dfs[seq(5,8)], .return = "full_models")
post_plots("tgdur", dfs[seq(5,8)], make_plot_func = pp_check, .return = "full_models")
```

### Nested models

Effects of subj and obj nested within each quantifier.

```{r tgdur2 }
res %>%
  filter(source == "tgdur_nested_models.csv") %>%
  select(-source) %>%
  kable()
```


```{r pps_tgdur2, results = "markup" }
post_plots("tgdur", dfs[seq(5,8)], .return = "nested_models")
post_plots("tgdur", dfs[seq(5,8)], make_plot_func = pp_check, .return = "nested_models")
```

## Regressions

Probability of regression, `abs(gbck - 2)`. Bernoulli likelihood with logistic link, results on the logistic scale.

```{r gbck }
res %>%
  filter(source == "gbck_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_gbck, results = "markup" }
post_plots("gbck", dfs, .return = "full_models")
post_plots("gbck", dfs, make_plot_func = pp_check, .return = "full_models")
```

### Nested models

Effects of subj and obj nested within each quantifier.

```{r gbck2 }
res %>%
  filter(source == "gbck_nested_models.csv") %>%
  select(-source) %>%
  kable()
```


```{r pps_gbck2, results = "markup" }
post_plots("gbck", dfs, .return = "nested_models")
post_plots("gbck", dfs, make_plot_func = pp_check, .return = "nested_models")
```


## Re-readings

`rr`. probability of re-reading  
Bernoulli likelihood with logistic link, results on the logistic scale.

```{r rr }
res %>%
  filter(source == "rr_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_rr, results = "markup" }
post_plots("rr", dfs, .return = "full_models")
post_plots("rr", dfs, make_plot_func = pp_check, .return = "full_models")
```

### Split models

Effects of subj and obj nested within each quantifier.

```{r rr2 }
res %>%
  filter(source == "rr_nested_models.csv") %>%
  select(-source) %>%
  kable()
```


```{r pps_rr2, results = "markup" }
post_plots("rr", dfs, .return = "nested_models")
post_plots("rr", dfs, make_plot_func = pp_check, .return = "nested_models")
```
